\documentclass{book}

\begin{document}
acknowledgments

Although my name is on the cover, The Book of F\# wouldn’t have been possible without the efforts of numerous people.

First, I need to thank the team at No Starch Press. Without them, writing a book would still be an item on my bucket list. In particular, I need to thank Bill Pollock and Alison Law. Bill’s encouragement, especially early in the process, gave this first-time author the confidence to take on this project. Alison’s experience was invaluable as she guided me through the waters of the publishing world and helped me prioritize the work.

To my good friend and official technical reviewer, Kevin Miller: thank you, thank you, thank you. Kevin went well beyond what I ever expected by taking as many as five passes over each chapter and regularly diving into the F\# language spec in his attempts to find errors within the text and the code samples. Beyond his technical review duties, Kevin often acted as a sounding board for my sometimes crazy ideas. His dedication, suggestions, and attention to detail helped shape this book, and for that I’m truly grateful.

Another big thank you to Tomas Petricek. His community involvement and willingness to share his deep knowledge of F\# was invaluableto me when I began learning the language. Tomas’s technical review of Chapters 11 and 12 really helped smooth out some of the rough edges, and this book has benefited greatly from his input.

Next, thank you to my friends and coworkers, who put up with months of my talking about F\# and the writing process. (Sorry, you haven’t heard the last of it, either!) In particular, I need to thank Brian Kline. Brian read every word of this book as someone wanting to learn F\#. No matter how many times I read through a chapter, he always managed to find a few typographical errors or point out areas where different wording would improve the message.

I’d never have had the opportunity to write this book if F\# didn’t exist. For that, I thank the F\# team for creating such an incredible language. Along those lines, I owe a debt of gratitude to the F\# community for being so welcoming and engaging. Without the many community resources available to help people get started with F\#, I don’t know that I’d have ever adopted it as part of my toolkit.

Finally, thank you to the people who were affected the most by this project: my family. I need to thank my parents not only for giving me life (as my mother likes to remind me), but also for letting me regularly take over a room in their house and escape into the creative process during weekend visits. Of course, I don’t know if I could have completed this project without the love and support of my wife, Esther, and my daughter, Nadia. Thank you for understanding the late nights and reclusive weekends that were necessary to make this dream a reality. I love you all.
\end{document}
