\documentclass{book}
\usepackage{xeCJK}
\setCJKmainfont{WenQuanYi Micro Hei}
\begin{document}

\pagestyle{empty}
\title{The Book\\of F\\Breaking Free with Managed \\Functional Programming}
\author{by Dave Fancher}
\maketitle

% pic

San Francisco








The Book of F\verb|#|. Copyright © 2014 by Dave Fancher.
All rights reserved. No part of this work may be reproduced or transmitted in any form or by any means, electronic
or mechanical, including photocopying, recording, or by any information storage or retrieval system, without the
prior written permission of the copyright owner and the publisher.
Printed in USA
First printing
18 17 16 15 14   1 2 3 4 5 6 7 8 9
ISBN-10: 1-59327-552-8
ISBN-13: 978-1-59327-552-5
Publisher: William Pollock
Production Editor: Alison Law
Cover Illustration: Chris Gould
Interior Design: Octopod Studios
Developmental Editors: Seph Kramer and William Pollock
Technical Reviewers: Kevin Miller and Tomas Petricek
Copyeditor: Rachel Monaghan
Compositors: Laurel Chun and Susan Glinert Stevens
Proofreader: James Fraleigh
For information on distribution, translations, or bulk sales, please contact No Starch Press, Inc. directly:
No Starch Press, Inc.
245 8th Street, San Francisco, CA 94103
phone: 415.863.9900; fax: 415.863.9950; info@nostarch.com; www.nostarch.com
Library of Congress Cataloging-in-Publication Data
Fancher, Dave.
The book of F\verb|#| : breaking free with managed functional programming / by Dave Fancher.
pages cm
Includes index.
ISBN 978-1-59327-552-5 -- ISBN 1-59327-552-8
1. F\verb|#| (Computer program language) I. Title. II. Title: Book of F-sharp.
QA76.73.F163F36 2014
005.1'17--dc23
2014000831
No Starch Press and the No Starch Press logo are registered trademarks of No Starch Press, Inc. Other product and
company names mentioned herein may be the trademarks of their respective owners. Rather than use a trademark
symbol with every occurrence of a trademarked name, we are using the names only in an editorial fashion and to
the benefit of the trademark owner, with no intention of infringement of the trademark.
The information in this book is distributed on an “As Is” basis, without warranty. While every precaution has been
taken in the preparation of this work, neither the author nor No Starch Press, Inc. shall have any liability to any
person or entity with respect to any loss or damage caused or alleged to be caused directly or indirectly by the infor-
mation contained in it.



\chapter{About the Author}
About the Author
Dave Fancher has been developing soft-
ware with the .NET Framework for more
than a decade. He is a familiar face in
the Indiana development community as
both a speaker and participant in user
groups around the state. In July 2013,
Dave was recognized as a Microsoft MVP
(Most Valuable Professional) for Visual F\verb|#|.
When not writing code or writing about
code at davefancher.com, he can often be
found watching a movie or gaming on his
Xbox One.

About the Technical Reviewer
Over the last 14 years, Kevin Miller has
worked on exciting projects with truly great
people while unsuccessfully pleading with
compilers to break their steadfast rules. He
enjoys studying the inherent beauty of logic,
and when inspired by the muses, actually
codes something deserving a modicum of
pride from time to time. His interests lie in
security, distributed systems, and data, but
he has a short attention ... squirrel!


Brief Content s
Foreword by Bryan Hunter ............................................... xv
Prefac............................................................. xix
Acknowledgments ..................................................... xxi
Introductio......................................................... xxiii
Chapter 1: Meet F\verb|#| ..................................................... 1
Chapter 2: F\verb|#| Interactive ................................................ 13
Chapter 3: Fundamentals ................................................ 25
Chapter 4: Staying Objective ............................................. 63
Chapter 5: Let’s Get Functional ........................................... 103
Chapter 6: Going to Collections .......................................... 133
Chapter 7: Patterns, Patterns, Everywher.................................... 159
Chapter 8: Measuring U............................................... 177
Chapter 9: Can I Quote You on That? ...................................... 187
Chapter 10: Show Me the Dat........................................... 201
Chapter 11: Asynchronous and Parallel Programming ........................... 229
Chapter 12: Computation Expressions ...................................... 257
Index ............................................................. 271




\end{document}
